Controlling the rheological properties of well-defined polyelectrolytes hydrogels by fine tuning their ion pairing process

### 2016-01-06 PALSE/ion_pairing_paper.tex
fig:dsc
caption of fig:dsc

\begin{scheme}
\includegraphics{synthesis.pdf}
\caption{Synthesis of \ce{PIm+Br-} and \ce{Ppyr+Br-} and their intermediate. $n=70$}
\label{sch:synthesis}
\end{scheme}

@@

\begin{figure}
\caption{DSC analysis of a crystalline polymer samples showing the presence of melting point.}
\label{fig:dsc}
\end{figure}

>>>>

\begin{scheme}
\includegraphics{synthesis.pdf}
\caption{Synthesis of \ce{PIm+Br-} and \ce{PPyr+Br-} and their intermediates \ce{POH} and \ce{PBr}. $n=70$}
\label{sch:synthesis}
\end{scheme}

@@

\begin{figure}
\includegraphics{dsc.pdf}
\caption{DSC measurements of polymer samples showing the presence of a melting point. Curves are shifted vertically by arbitrary amounts for clarity.}
\label{fig:dsc}
\end{figure}
